Cauchy example

### 2020-03-26 src/s_cauchy.Rmd
finished draft of Cauchy section

Compare nominal and alt parameterisations
```{r}
b_df <- 
  tibble(iteration=iter,
         middle=r_vals,
         lower=r_vals_lower,
         upper=r_vals_upper,
         variable="alt") %>% 
  bind_rows(tibble(iteration=iter,
         middle=r_vals1,
         lower=r_vals1_lower,
         upper=r_vals1_upper,
         variable="nom"))
# saveRDS(b_df, "../output/cauchy_r_squared.rds")
g1 <- b_df %>% 
  ggplot(aes(x=iteration)) +
  geom_point(aes(y=middle,colour=as.factor(variable))) +
  geom_line(aes(y=middle,colour=as.factor(variable))) +
  ylim(NA, 1) +
  ylab(TeX("$R^2$")) +
  scale_color_brewer("Parameterisation", palette = "Dark2", labels=c("Alternative", "Nominal")) +
  xlab("Iteration") +
  theme(text=element_text(size=11, colour="black"),
        axis.text = element_text(size=10, colour="black"),
        legend.position = "none",
        axis.title.y = element_blank()) +
  scale_x_log10() +
  ggtitle(TeX("Quantile $R^2$"))
g1
```

@@

```{r}
g2 <- 
  a_df %>% 
  melt(id.vars="iteration") %>% 
  ggplot(aes(x=iteration, y=value, colour=as.factor(variable))) +
  geom_point() +
  geom_line() +
  ylab(TeX("$R^*$")) +
  scale_color_brewer("Parameterisation", palette = "Dark2", labels=c("Alternative", "Nominal")) +
  xlab("Iteration") +
  theme(text=element_text(size=11, colour="black"),
        axis.text = element_text(size=10, colour="black"),
        legend.position = c(0.8, 0.8),
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_x_log10() +
  scale_y_continuous(limits=c(0.8, NA), breaks = seq(1, 7, 1)) +
  ggtitle(TeX("Split-$R^*$"))
g2
```

@@

c_df <- 
  tibble(iteration=iter,
         middle=r_hat1,
         lower=r_hat1_lower,
         upper=r_hat1_upper,
         variable="alt") %>% 
  bind_rows(tibble(iteration=iter,
         middle=r_hat,
         lower=r_hat_lower,
         upper=r_hat_upper,
         variable="nom"))
# saveRDS(c_df, "../output/cauchy_r_hat.rds")
g3 <- 
  c_df %>% 
  ggplot(aes(x=iteration)) +
  geom_point(aes(y=middle, colour=as.factor(variable))) +
  geom_line(aes(y=middle, colour=as.factor(variable))) +
  ylab(TeX("$\\hat{R}$")) +
  scale_color_brewer("Parameterisation", palette = "Dark2", labels=c("Alternative", "Nominal")) +
  scale_fill_brewer("Parameterisation", palette = "Dark2", labels=c("Alternative", "Nominal")) +
  xlab("Iteration") +
  theme(text=element_text(size=11, colour="black"),
        axis.text = element_text(size=10, colour="black"),
        legend.position = "none",
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_x_log10() +
  scale_y_continuous(limits=c(0.99, NA), breaks = seq(1, 6, 0.2)) +
  ggtitle(TeX("Max split-$\\hat{R}$"))
g3
```

Combine
```{r}
pdf("../output/cauchy_convergence.pdf", width = 12, height = 4)
multiplot(g1, g3, g2, cols = 3)
dev.off()
```

>>>>

Compare nominal and alt parameterisations
```{r}
b_df <- 
  tibble(iteration=iter,
         middle=r_vals,
         lower=r_vals_lower,
         upper=r_vals_upper,
         variable="alt") %>% 
  bind_rows(tibble(iteration=iter,
         middle=r_vals1,
         lower=r_vals1_lower,
         upper=r_vals1_upper,
         variable="nom"))
# saveRDS(b_df, "../output/cauchy_r_squared.rds")
b_df <- readRDS("../output/cauchy_r_squared.rds")
g1 <- b_df %>% 
  ggplot(aes(x=iteration)) +
  geom_point(aes(y=middle,colour=as.factor(variable))) +
  geom_line(aes(y=middle,colour=as.factor(variable))) +
  ylim(NA, 1) +
  ylab(TeX("$R^2$")) +
  scale_color_brewer("Parameterisation", palette = "Dark2", labels=c("Alternative", "Nominal")) +
  xlab("Iteration") +
  theme(text=element_text(size=11, colour="black"),
        axis.text = element_text(size=10, colour="black"),
        legend.position = "none",
        axis.title.y = element_blank()) +
  scale_x_log10() +
  ggtitle(TeX("A. Quantile $R^2$"))
g1
```

@@

```{r}
a_df <- readRDS("../output/cauchy_r_star.rds")
g2 <- 
  a_df %>% 
  melt(id.vars="iteration") %>% 
  ggplot(aes(x=iteration, y=value, colour=as.factor(variable))) +
  geom_point() +
  geom_line() +
  ylab(TeX("$R^*$")) +
  scale_color_brewer("Parameterisation", palette = "Dark2", labels=c("Alternative", "Nominal")) +
  xlab("Iteration") +
  theme(text=element_text(size=11, colour="black"),
        axis.text = element_text(size=10, colour="black"),
        legend.position = c(0.8, 0.8),
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_x_log10() +
  scale_y_continuous(limits=c(0.8, NA), breaks = seq(1, 7, 1)) +
  ggtitle(TeX("D. Split-$R^*$"))
g2
```

@@

c_df <- 
  tibble(iteration=iter,
         middle=r_hat1,
         lower=r_hat1_lower,
         upper=r_hat1_upper,
         variable="alt") %>% 
  bind_rows(tibble(iteration=iter,
         middle=r_hat,
         lower=r_hat_lower,
         upper=r_hat_upper,
         variable="nom"))
# saveRDS(c_df, "../output/cauchy_r_hat.rds")
c_df <- readRDS("../output/cauchy_r_hat.rds")
g3 <- 
  c_df %>% 
  ggplot(aes(x=iteration)) +
  geom_point(aes(y=middle, colour=as.factor(variable))) +
  geom_line(aes(y=middle, colour=as.factor(variable))) +
  ylab(TeX("$\\hat{R}$")) +
  scale_color_brewer("Parameterisation", palette = "Dark2", labels=c("Alternative", "Nominal")) +
  scale_fill_brewer("Parameterisation", palette = "Dark2", labels=c("Alternative", "Nominal")) +
  xlab("Iteration") +
  theme(text=element_text(size=11, colour="black"),
        axis.text = element_text(size=10, colour="black"),
        legend.position = "none",
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_x_log10() +
  scale_y_continuous(limits=c(0.99, NA), breaks = seq(1, 6, 0.2)) +
  ggtitle(TeX("B. Max split-$\\hat{R}$"))
g3
```

Multivariate Rhat
```{r}
fit1 <- readRDS("../output/fit_alt_50000.rds")
x <- rstan::extract(fit1, permuted=F, pars="x")
Rhat_alt <- map_dbl(iter, ~r_hat_multivariate(x[1:., , ]))

fit1 <- readRDS("../output/fit_nominal_50000.rds")
x <- rstan::extract(fit1, permuted=F, pars="x")
Rhat_nom <- map_dbl(iter, ~r_hat_multivariate(x[1:., , ]))
g_df <- tibble(iteration=iter,
       alt=Rhat_alt,
       nom=Rhat_nom) 
g4 <- 
  tibble(iteration=iter,
       alt=Rhat_alt,
       nom=Rhat_nom) %>% 
  melt(id.vars="iteration") %>% 
  ggplot(aes(x=iteration)) +
  geom_point(aes(y=value, colour=as.factor(variable))) +
  geom_line(aes(y=value, colour=as.factor(variable))) +
  ylab(TeX("$\\hat{R}$")) +
  scale_color_brewer("Parameterisation", palette = "Dark2", labels=c("Alternative", "Nominal")) +
  scale_fill_brewer("Parameterisation", palette = "Dark2", labels=c("Alternative", "Nominal")) +
  xlab("Iteration") +
  theme(text=element_text(size=11, colour="black"),
        axis.text = element_text(size=10, colour="black"),
        legend.position = "none",
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_x_log10() +
  scale_y_continuous(limits=c(0.99, NA), breaks = seq(1, 6, 0.2)) +
  ggtitle(TeX("C. Multivariate split-$\\hat{R}$"))
```

Tail ESS
```{r}
fit1 <- readRDS("../output/fit_alt_50000.rds")
x <- rstan::extract(fit1, permuted=F, pars="x")
tail_ess_alt <- map_dbl(iter, function(i) min(map_dbl(seq(1, 50, 1), ~ess_tail(x[1:i, , .]))))
bulk_ess_alt <- map_dbl(iter, function(i) min(map_dbl(seq(1, 50, 1), ~ess_bulk(x[1:i, , .]))))

fit1 <- readRDS("../output/fit_nominal_50000.rds")
x <- rstan::extract(fit1, permuted=F, pars="x")
tail_ess_nom <- map_dbl(iter, function(i) min(map_dbl(seq(1, 50, 1), ~ess_tail(x[1:i, , .]))))
bulk_ess_nom <- map_dbl(iter, function(i) min(map_dbl(seq(1, 50, 1), ~ess_bulk(x[1:i, , .]))))

e_df <- tibble(iteration=iter,
               alt=tail_ess_alt,
               nom=tail_ess_nom)
saveRDS(e_df, "../output/cauchy_tail_ess.rds")
f_df <- tibble(iteration=iter,
               alt=bulk_ess_alt,
               nom=bulk_ess_nom)
saveRDS(f_df, "../output/cauchy_bulk_ess.rds")
g5 <- 
  e_df %>% 
  melt(id.vars="iteration") %>% 
  ggplot(aes(x=iteration)) +
  geom_point(aes(y=value, colour=as.factor(variable))) +
  geom_line(aes(y=value, colour=as.factor(variable))) +
  scale_color_brewer("Parameterisation", palette = "Dark2", labels=c("Alternative", "Nominal")) +
  scale_fill_brewer("Parameterisation", palette = "Dark2", labels=c("Alternative", "Nominal")) +
  xlab("Iteration") +
  theme(text=element_text(size=11, colour="black"),
        axis.text = element_text(size=10, colour="black"),
        legend.position = "none",
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 400, linetype=2) +
  scale_x_log10() +
  scale_y_log10() +
  ggtitle(TeX("E. Tail ESS"))

g6 <- 
  f_df %>% 
  melt(id.vars="iteration") %>% 
  ggplot(aes(x=iteration)) +
  geom_point(aes(y=value, colour=as.factor(variable))) +
  geom_line(aes(y=value, colour=as.factor(variable))) +
  scale_color_brewer("Parameterisation", palette = "Dark2", labels=c("Alternative", "Nominal")) +
  scale_fill_brewer("Parameterisation", palette = "Dark2", labels=c("Alternative", "Nominal")) +
  xlab("Iteration") +
  theme(text=element_text(size=11, colour="black"),
        axis.text = element_text(size=10, colour="black"),
        legend.position = "none",
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 400, linetype=2) +
  scale_x_log10() +
  scale_y_log10() +
  ggtitle(TeX("F. Bulk ESS"))
```

Combine
```{r}
pdf("../output/cauchy_convergence.pdf", width = 12, height = 8)
multiplot(g1, g4, g5, g3, g2, g6, cols = 2)
dev.off()
```
